---
title: "AMSA-HW1"
author: 
- 'ID : 111024517'
- 'Name : 鄭家豪'
date: due on 02/23
geometry: left=3cm,right=3cm,top=2cm,bottom=2cm
header-includes:
  - \usepackage{leading}
  - \leading{18pt}
  - \usepackage{xeCJK}
  - \setCJKmainfont{標楷體}
  - \setCJKmonofont{標楷體}
output:
  pdf_document:
    latex_engine: xelatex
classoption: a4paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

# About Data  

Accroding to WHO,stroke is the 2nd leading cause of death globally.  
This dataset is used to predict whether a patient is likely to get stoke based on the 11 clinical features.

The resourse : https://www.kaggle.com/datasets/fedesoriano/stroke-prediction-dataset


# Attribute Information
 
* (discrete)id: unique identifier
* (discrete)gender: "Male", "Female" or "Other"
* (continuous)age: age of the patient
* (discrete)hypertension: 0 if the patient doesn't have hypertension, 1 if the patient has hypertension
* (discrete)heart_disease: 0 if the patient doesn't have any heart diseases, 1 if the patient has a heart disease
* (discrete)ever_married: "No" or "Yes"
* (discrete)work_type: "children", "Govt_jov", "Never_worked", "Private" or "Self-employed"
* (discrete)Residence_type: "Rural" or "Urban"
* (continuous)avg_glucose_level: average glucose level in blood
* (continuous)bmi: body mass index
* (discrete)smoking_status: "formerly smoked", "never smoked", "smokes" or "Unknown"
* (discrete)stroke: 1 if the patient had a stroke or 0 if not

# Simple EDA

## Check data

```{r echo=FALSE}
data <- read.csv("111024517_healthcare-dataset-stroke-data.csv",
                 header = T)
str(data)
```

 From the above , we find the "NA" value in bmi variable.We chose to remove all NA's , assuming that they are not important for the analysis . Then , obtained :  
 
```{r removing Na value, echo=FALSE}
data_new <- data[-c(which(data$bmi %in% c("N/A"))),]
data_new$bmi <- as.numeric(data_new$bmi)
str(data_new)
```
 
 Here we have 4909 observations and 12 variables after removing the row data containing the NA values.
 
## Scatter plot(Analysis of the sampling distribution)
```{r echo=FALSE}
#scatter plot (x:age;y:bmi;factor=gender)
ggplot(data_new, aes(x = age, y = bmi, color = gender)) +
  geom_jitter()
```

 這裡展示出 age-bmi 的 scatter plot 且以 gender來區別每個點的散佈狀況，可以大致上觀察出，年齡對於男女比例是差不多的且女生的BMI相對男生沒有明顯的落差，可能意味著收集資料時，針對不同年齡的男女bmi落差不會很顯著。不過有幾個 outlier 很明顯有所區別，其BMI值接近 100，屬於男性。  
 
## Boxplot(Analysis of information on smoking habits)
```{r echo=FALSE}
#boxplot ((x:gender;y:bmi;factor=stroke)
ggplot(data_new, aes(x = smoking_status, y = bmi, color = as.factor(stroke))) +
  geom_boxplot()
```
 
 這裡展示出 smoking_status-BMI 的 boxplot 且以 中風與否來做區別，主要是想了解，對於4種不同抽菸習慣，基於中風情況不同，bmi分布是否相似 ? 從上面可以看出，除了未知抽菸習慣有明顯的一點不同外，其他三種抽菸習慣的分布都蠻相似的。  
 
## Bubble plot(Analysis of information on glucose)
```{r echo=FALSE}
#Bubble plot (x:age ; y=agl;factor = stroke;size = bmi)
ggplot(data_new, aes(x = age, y =avg_glucose_level, size = bmi,color = as.factor(stroke))) +
  geom_point(alpha = 0.5) +
  scale_size(name = "bmi", range = c(1, 10))
```

 這裡展示出以 bmi大小表示 bubble形狀，age-血糖 的 Bubble plot ， 另外以中風與否來做區別。  
 這裡可以看出一些資訊，年齡大且平均血糖較高的人，較容易得到中風。另外，Bmi並沒有對於中風與否提供太明顯的區別，因為沒有中風的人當中，具有高Bmi的人是佔多數，以及中風的人當中，bmi值似乎都差不多。
