---
title: "Applied Multivariate analysis-HW7"
author: 
- 'ID : 111024517'
- 'Name : 鄭家豪'
geometry: left=3cm,right=3cm,top=2cm,bottom=2cm
header-includes:
  - \usepackage{leading}
  - \leading{18pt}
  - \usepackage{xeCJK}
  - \setCJKmainfont{標楷體}
  - \setCJKmonofont{標楷體}
output:
  pdf_document:
    latex_engine: xelatex
classoption: a4paper
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE,
	comment = ""
)
```

# Pre-processing  
## Check missing value  
From the data description, we know that the variable gender = 9 means Missing value, so calculating how many Missing values:    
```{r echo=FALSE}
library("readxl")
data <- read_excel("womenraw.xls")
cat("The sum of gender is 9(meaning missing):",sum(data$G==9),"\n")
cat("The total observation of womenraw dataset:",dim(data)[1])
```

Here we know that there are 37 Missing values, which is not a large number compared to the total number of samples, so we choose to remove these 37 samples here.

## Construct contingency table  

Using the data that has removed the Missing value to integrate into contingency table:(code in Appendix)  
```{r echo=FALSE}
library(kableExtra)
library(tidyverse)
rm.data <- data[-which(data$G == 9),]
mat <- xtabs(~rm.data$C+rm.data$G+rm.data$A+rm.data$Q3,data=rm.data)
mat <- data.frame(mat)
colnames(mat) <- c("C","G","A","Q3","Freq")
contingency.mat <- matrix(0,nrow = 24*2*6,ncol = 4)
for (i in 1:4){
  index <- sort(unique(mat$Q3))[i]
  contingency.mat[,i] <- mat$Freq[which(mat$Q3==i)]
}
contingency.mat <- data.frame(contingency.mat)
colnames(contingency.mat) =c("W","w","H","?") 
con.mat <- cbind(mat[1:288,1:3],contingency.mat)
omit = matrix(rep("...", ncol(con.mat)*2), nrow = 2)
colnames(omit) <- colnames(con.mat)
a <- which(mat$C == 16 & mat$G == 1 & mat$A == 2 & mat$Q3==1) 
print <- rbind(con.mat[1:2,],omit,con.mat[a,],omit,con.mat[287:288,])
kable(print,row.names = FALSE) %>%
add_header_above(c(" ", " ", " ", "Q3" = 4))
```

**(Note:The PLm<26-35 for coding is (C,G,A)= (16,1,2)**

# Corresponding Analysis

**CA plot:** The coding is attached in Appendix

```{r echo=FALSE}
library(ca)
ca = ca(contingency.mat)
principal.coord <- cacoord(ca,type="rowprincipal") 
row.coord <-  principal.coord$rows 
plot(x = row.coord[,1],y=-row.coord[,2],pch=16,col="black",
     xlab="",ylab="",xlim=c(-1.1,2.1),ylim=c(-1,1.5))  
mtext(paste0("Dim1:",100*round((ca$sv^2)[1]/sum(ca$rowinertia),4),"%"),
      side=1, line=2.5) 
mtext(paste0("Dim2:",100*round((ca$sv^2)[2]/sum(ca$rowinertia),4),"%"), 
      side=2, line=2.5) 
points(x = ca$colcoord[,1],y = -ca$colcoord[,2],col="red",pch=17)
text(x=ca$colcoord[,1],y=-ca$colcoord[,2],cex = c(2,1.5,2,4),
     labels = c("W","w","H","?"),col = c("red","red","red","red"))
points(x = row.coord[a,1],y = -row.coord[a,2],
       col="blue",pch = 1,cex=1.5)
text(x= row.coord[a,1],y =-row.coord[a,2] + 0.1 ,cex=1,
     labels = "PLm < 26-35",col="blue")
```

# Appendix

```{r eval=FALSE}
# Read data
library("readxl")
data <- read_excel("womenraw.xls")
cat("The sum of gender is 9(meaning missing):",sum(data$G==9),"\n")
cat("The total observation of womenraw dataset:",dim(data)[1])

# Contingency table
library(kableExtra)
library(tidyverse)
rm.data <- data[-which(data$G == 9),]
mat <- xtabs(~rm.data$C+rm.data$G+rm.data$A+rm.data$Q3,data=rm.data)
mat <- data.frame(mat)
colnames(mat) <- c("C","G","A","Q3","Freq")
contingency.mat <- matrix(0,nrow = 24*2*6,ncol = 4)
for (i in 1:4){
  index <- sort(unique(mat$Q3))[i]
  contingency.mat[,i] <- mat$Freq[which(mat$Q3==i)]
}
contingency.mat <- data.frame(contingency.mat)
colnames(contingency.mat) =c("W","w","H","?") 
con.mat <- cbind(mat[1:288,1:3],contingency.mat)
omit = matrix(rep("...", ncol(con.mat)*2), nrow = 2)
colnames(omit) <- colnames(con.mat)
a <- which(mat$C == 16 & mat$G == 1 & mat$A == 2 & mat$Q3==1) 
print <- rbind(con.mat[1:2,],omit,con.mat[a,],omit,con.mat[287:288,])
kable(print,row.names = FALSE) %>%
add_header_above(c(" ", " ", " ", "Q3" = 4))

# CA plot
library(ca)
ca = ca(contingency.mat)
principal.coord <- cacoord(ca,type="rowprincipal") 
row.coord <-  principal.coord$rows 
plot(x = row.coord[,1],y=-row.coord[,2],pch=16,col="black",
     xlab="",ylab="",xlim=c(-1.1,2.1),ylim=c(-1,1.5))  
mtext(paste0("Dim1:",100*round((ca$sv^2)[1]/sum(ca$rowinertia),4),"%"),
      side=1, line=2.5) 
mtext(paste0("Dim2:",100*round((ca$sv^2)[2]/sum(ca$rowinertia),4),"%"), 
      side=2, line=2.5) 
points(x = ca$colcoord[,1],y = -ca$colcoord[,2],col="red",pch=17)
text(x=ca$colcoord[,1],y=-ca$colcoord[,2],cex = c(2,1.5,2,4),
     labels = c("W","w","H","?"),col = c("red","red","red","red"))
points(x = row.coord[a,1],y = -row.coord[a,2],
       col="blue",pch = 1,cex=1.5)
text(x= row.coord[a,1],y =-row.coord[a,2] + 0.1 ,cex=1,
     labels = "PLm < 26-35",col="blue")
```

